Limited plasticity but increased variance in physiological rates across ectotherm populations under climate change

### 2025-01-01 ms.qmd
Update supp with R1 comments

@@

@@

We split the screening of titles and abstracts for the 1,321 papers found in our search among DWAN, FK, FS, and SN evenly. To ensure consistency among authors in title and abstract inclusion, relevant authors went through a randomly selected set of papers together before the formal screening to calibrate selection of papers based on our inclusion criteria (see below). In cases of disagreement regarding inclusion, we conservatively included the paper for full text screening and discussed uncertain papers among authors to come to a decision. After title and abstract screening, there was a total of 149 papers for full text screening. Papers were included only if they: 1) measured a physiological rate acutely at two temperatures on a sample of animals chronically exposed to the same two temperatures for at least 1 week; and 2) where physiological rates measured were burst and sustained locomotion, metabolic rates (standard, resting, routine and maximal), heart rates, and/or enzyme activities. Importantly, as in @Seebacher2015-wi, we only included studies that manipulated temperatures within normal thermal ranges for the species.

@@

@@

@@

  ggsave(accl_time, file = "./output/figures/figS3.png", height = 6, width = 8.5)

@@

#### **Acute and acclimation for detailed trait categories across marine, freshwater and terrestrial taxa**

Across habitats, the extent to which whole-organism versus biochemical traits acclimated varied ("Model 3"; [@fig-btrait]A-C). Biochemical traits acclimated to a greater extent compared to whole-organism traits in marine habitats ([@fig-btrait]B), whereas both whole-organism and biochemical traits acclimated similarly in freshwater ectotherms ([@fig-btrait]C). Neither trait category acclimated in terrestrial ectotherms ([@fig-btrait]A).

>>>>

# Look at life stages and trait type distribution
#life_trait <- lnRRQ10_data %>% group_by(life.hist, trait_broad, habitat) %>% summarise(n=n()) %>% arrange(habitat)
#colnames(life_trait) <- c("Life Stage", "Trait Category", "Habitat", "# of Effects")
#flextable(life_trait) %>% save_as_docx(path = "./output/tables/table.docx")

@@

# Slopes for max temp and acclimation time
  acc_time_slope_model1.2 <- posteriors_1.2[,"b_c_accl_time"]
  max_temp_slope_model1.2 <- posteriors_1.2[,"b_max_temp_c"]

@@

We split the screening of titles and abstracts for the 1,321 papers found in our search among DWAN, FK, FS, and SN evenly. To ensure consistency among authors in title and abstract inclusion, relevant authors went through a randomly selected set of papers together before the formal screening to calibrate selection of papers based on our inclusion criteria (see below). In cases of disagreement regarding inclusion, we conservatively included the paper for full text screening and discussed uncertain papers among authors to come to a decision. After title and abstract screening, there was a total of 149 papers for full text screening. Papers were included only if they: 1) measured a physiological rate at two temperatures on a sample of animals chronically exposed to the same two temperatures for at least 1 week. Studies had to measure, following acclimation, physiological rates at acute temperatures that at least matched acclimation temperatures, but often measurements were fully factorial allowing for both acclimated and acute measurements to be extracted; and 2) where physiological rates measured were burst and sustained locomotion, metabolic rates (standard, resting, routine and maximal), heart rates, and/or enzyme activities. Importantly, as in @Seebacher2015-wi, we only included studies that manipulated temperatures within normal thermal ranges for the species because we expected stressful temperatures would impact physiological rates. We determined which temperatures coincided with normal thermal ranges using information within the study (i.e., self-reported) or, when not provided, information from the internet on typical activity temperatures (e.g., Wikipedia or Google searches). This criterion meant that we often only had a single data set (1 acclimated and 2 acute measurements) for each paper.

@@

As predicted, we did find evidence that $lnRR_{Q_{10}}$ was impacted by the maximum temperature used within a study, but this effect was small (Slope from "Model 2": `r mean (max_temp_slope_model1.2)`, 95% CI: `r quantile(max_temp_slope_model1.2, 0.025)` to `r quantile(max_temp_slope_model1.2, 0.975)`, $p_{MCMC}$ = `r round(pmcmc(max_temp_slope_model1.2), digit = 4)`, @fig-lnrrq10_temp). Regardless, we control for maximum temperature in all our models.

@@

While we control for acclimation time in all our models, it did not impact $lnRR_{Q_{10}}$ (Slope from "Model 2": `r mean (acc_time_slope_model1.2)`, 95% CI: `r quantile(acc_time_slope_model1.2, 0.025)` to `r quantile(acc_time_slope_model1.2, 0.975)`, $p_{MCMC}$ = `r round(pmcmc(acc_time_slope_model1.2), digit = 4)`, @fig-accl_time)

@@

  ggsave(accl_time, file = "./output/figures/figS3.png", height = 6, width = 12)

@@

#### **Acute and acclimation for trait categories across marine, freshwater and terrestrial taxa**

Across habitats, the extent to which whole-organism versus biochemical traits acclimated varied ("Model 3"; [@fig-btrait]A-C). Biochemical traits acclimated to a greater extent compared to whole-organism traits in marine habitats ([@fig-btrait]B), whereas both whole-organism and biochemical traits acclimated similarly in freshwater ectotherms ([@fig-btrait]C). Neither trait category acclimated in terrestrial ectotherms ([@fig-btrait]A). However, there were no biochemical traits measured for juveniles in terrestrial species confounding life stage and trat category – though there were no differences between adult and juveniles in any case (see results in main manuscript).
